---
title: Student Demands
author: ''
date: '2020-07-31'
slug: student-demands
categories: []
tags: []
---

```{r setup, include = FALSE}
library(tidyverse)
library(DT)
library(googlesheets4)

knitr::opts_chunk$set(echo = FALSE)

link <- function(link, title) ifelse(is.na(link), "", glue::glue("<a href='{link}' target='_blank'>{title}</a>"))

df <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1NSiHmcJOFq8nlYVPxURbEE8uK1GFGRXXQFm87dSdN1Q/edit?usp=sharing", sheet = "Web Database") %>%
  arrange(desc(Date)) %>%
  mutate(Link = link(Link, `Link Title`),
         Date = str_replace(strftime(Date, "%B %e, %Y"), "  ", " "),
         `Other Links` = str_replace_all(`Other Links`, "\n", "<br/>"))

```

<div class='intro'>
<div class='center'>

The Covid-19 epidemic and the murder of George Floyd precipitated a wave of student activism in 2020. This website is a database of the demands students have presented to their educational institutions in response. The intention of the project is to document the work of student activists and to serve as a resource for activists drafting new campaigns at their institutions.

The database currently contains `r nrow(df)` documents from `r nrow(distinct(df, Institution))` institutions.

</div>
</div>


<br/>

```{r, message = FALSE}


df %>%
  select(`Institution`, `Department or Organization`, `Date`, `Link`, `Other Links`) %>%
  datatable(escape = FALSE, autoHideNavigation = TRUE)
```


<div class='center'>
<br/>

--------


## Contribute
If you know of a petition or set of demands that aren't in the database, please consider submitting it for inclusion: [Google Form](https://forms.gle/bfRPDoVzp3ydNiYT6).

<br/>

## Methodology
The database is organized around primary documents which describe demands to academic institutions.

_Scope_

Any demands presented to higher educational institutions since January 1, 2020. 


_Field Descriptions_

- **Institution**: The educational institution identified in the primary document.
- **Department or Organization**: In some cases students compose demands to their particular academic department, and in other cases target the whole institution. The source of the demand document, whether from a department or organization, is given in this column.
- **Date**: A date is included when a date is visible in the primary document. If multiple dates are listed (for example, if a document is updated) then the earliest date is listed. 
- **Link**: Links to the primary document with student demands. The link title is set to the title of the document when there is one, the Google Doc document name when it reads as a title, and otherwise the document source (Twitter, Google Doc) is used as a title.
- **Other Links**: Includes links to related news articles or websites affiliated with the petitioners.

<br/>

## About

</div>